BOLD Parameter Estimation Using Particle Filters

### 2010-07-21 doc/thesis/results.tex
corrected the intro, and moved the noise description out to methods

\chapter{Simulation}
Two levels of simulation are discussed in this section. First the simulation of single time series
and second, a slice of simulated FMRI time series. The single time series tests
are necessary to investigate the power of particle filters in 
identifying the BOLD model in a noisy environment. If the particle filter is unable
to get back to the "true" time-series in spite of noise then the particle filter
will not be useful. Additionally, determination of reasonable parameters from the
time-series is also desirable. The reason to then simulate an entire slice is that
the "Possum" FMRI simulation tool models noise more realistically, for instance by
adding spatial correlation. Additionally 
it provides insight into the applicability of particle filters in modeling the BOLD 
signal on a large scale. Both sorts of tests are usefull in determining the
consistency of the particle filter. For the single voxel tests, each test will
actually be performed eleven different times, each with a new noise realization.
If runs fail to have consistent estimates of the underlying BOLD signal, then
this would indicate a large variance error in the model. Similarly, in the
Possum simulation there are actually only four discrete parameter sets driving the time-series.
Nevertheless each voxel will have a different tissue composition and a different
noise realization. Therefore the Possum simulation should also provide a good
test of the consistency of the BOLD model.

\section{Single Time Series}
\label{sec:Single Voxel Simulation}
Given the state-space equations for the BOLD signal, simulating a single time 
series is relatively straight forward. After a "true" signal is generated,
identically and independently distributed (I.I.D.) Gaussian noise and a Wiener
process with Gaussian I.I.D. steps are added to the true signal. Finally a 
"carrier level" is added, since BOLD is typically
measured as a \% difference from the baseline. The particle filter
algorithm will immediately remove this by calculating the \% difference, 
but adding a carrier level means that the exact same algorithm which 
will is used for simulated data may be used for the real data.

Once this noisy simulated time series has been generated, the particle filter algorithm
 is then run on this single time series "image". Here I will include two sets of tests 
to determine the power of the particle filter in modeling. The first set are 
used to demonstrate the ability of the particle filter to find the most likely
set of parameters/state variables over the course of the run. The second type
of test will investigate the problem of false-positives. As the first
round of tests will show, given that there is an underlying BOLD signal, 
the particle filter is excellent at finding the most probable cause of 
the observed signal. However, as discussed in the false positive tests,
even if there is no true underlying signal, the particle filter will still determine
the most likely BOLD signal; which may not be flat. Thus, it is 
important to investigate methods of determining false positives using 
average residuals. This problem could in actuality never come up, for instance
if the number of measurements is very large or if the noise peaks are not
particularly large.

@@

To begin the single voxel simulation; I generated a signal using the following parameters:
$\{\tau_0 = 1.45, \alpha = .3, E_0 = .47, V_0 = .044, \tau_s = 1.94, \tau_f = 1.99, \epsilon = 1.8\}$.
These same parameters will be used again in the high noise case. The noise realizations were
then based on a measurement noise, $\sigma_y$, of $.001$ and a drift standard deviation,
$\sigma_x$ of $.0005$. The measurement noise as well as the steps of the drift
were taken to be Gaussian
For this low noise case, the eleven realizations are shown in \autoref{fig:LowNoiseRealization}.
The actual signal that was delivered into the particle filter
is the result of some preprocessing to remove drift, as described in 
\autoref{sec:Methods Preprocessing}. The bias introduced into the signal by preprocessing 
may have some effect on the resulting fit; thus the preprocessed signal is compared
to the true BOLD signal in \autoref{fig:PreprocessedLowNoise}.
The preprocessing consists of several steps, which are discussed in detail in \autoref{sec:Methods Preprocessing}.
Obviously the spline struggles to match the signal near the end, as the graph shows, although 
overall, the preprocessing seems to have been successful at removing trends. Finally, the 
set of fits to the true BOLD signal are shown in \autoref{fig:FitComparisonLowNoise}.
The filtering property of the particle filter is clear from the results here.  In several locations the output
of the particle filter looks like a filtered version of the input. For instance toward the
end, the estimates stay flat in spite of the preprocessed data drifting off. By
this point, the algorithm has converged sufficiently to know that that such a movement in
signal isn't possible. A similar circumstance occurs at 100 seconds in. 
In general the fits are good, although the bias introduced by pre-processing clearly
results in a slightly larger peak signal. The final parameter sets are shown in 
\autoref{tab:LowNoiseResults}.

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline 
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & $\sqrt{MSR}$ &$\sqrt{MSE}$\\
\hline 
\rowcolor[gray]{.8}
1.45 & .3 & .47 & .044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline 
\hline 
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.009876  \\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.009932  \\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.009680  \\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.009120  \\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.009713  \\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.009485  \\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.010219  \\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.010080  \\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.010329  \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.010015  \\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.009505  \\
\hline                                                                           
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.009814 \\
\hline 
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise. First row is the true parameters,
last is mean over the 11 runs. The $\sqrt{MSR}$ is the square root of the mean square of the
residuals. Although in real data I won't distinguish between residual and error, here I will.
$\sqrt{MSE}$ is the mean squared difference between the true signal and the estimated signal.
This is the actual error, due to a combination of noise and preprocessing. }
\label{tab:LowNoiseResults} 
\end{table}

@@

The parameters arrived at for all ten filter runs are shown in \autoref{tab:HighNoiseResults}.
Clearly the additional noise have resulted in much more sporadic results. This is often the 
result when the particle filter converges too fast, a result of the weighting functions' variance
being significantly smaller than the measurement noise ($.005$ vs. $.01$). The square-root
MSE certainly suffers due to this effect.

%NO SIGNAL, LOW NOISE
\subsection{Pure-Noise, low magnitude}
\label{sec:PureNoiseLowMag}
The two final single-voxel tests force the particle filter to attempt to "learn" a noise-only
time series. In the first test the noise used will be the same as that from the \autoref{sec:HighNoise},
$\sigma_x = .01, \sigma_y = .005$. The parameters will be set the same as well, but the
stimulus/input will be set to 0 the entire time. In effect it is a region of the brain for
which no visual stimulus induces activity. For the particle filter, on the other hand,
the stimulus will be left as in the previous two sections. The question then is how the
particle filter will respond to signal that does not correlate with the input, and how
the output may be differentiated from a time series that does. The time series'
are shown in \autoref{fig:NoiseOnly}, the preprocessed versions are shown in \autoref{fig:PreprocessedNoiseOnly}.
The line fits are shown in \autoref{fig:fits_noiseonly}.

@@

As before, the convergence all seems to follow a similar path, leaving almost no
variance in the estimated time series (\autoref{fig:fits_noiseonly_high}). Now, however
the peaks are comparable to peaks in a "real" timeseries. Interestingly the algorithm
suffered from almost constant particle deprevation, meaning that the heuristic
for rescuing the particle filter from particle deprivation, discuessed in
\autoref{sec:Resampling} in fact was working against the proper course of action. Of course
 the proper course of action in this case would be for the particle filter to fail,
 since no particle can really properly estimate a random sequence. When this mechanism
 was removed, all 11 runs stopped due to particle deprevation (all weights hit zero). 
 The problem with allowing particle deprivation to occur is that it can \emph{rarely}
 occur if the prior happens to not be dense enough in the area of the solution. Thus,
 there is an issue of false positives vs. false negatives. A middle ground, such as 
 allowing deprivation to occur if the recovery mechanism has already triggered once
 may be an acceptable compromise, however it would be difficult to strike the 
 right balance. Instead for the purposes here we depend on the square root MSR to 
 evaluate if the results were reasonable or not.

@@

The first step in determining the validity of a model to provide and order of quality
to rate the results by. Unfortunately, because of the variablity in the signal levels the
raw $\sqrt{MSR}$ cannot perform this task. As demonstrated by \autoref{sec:PureNoiseLowMag},
just because the square-root mean-squared-residual is low doesn't mean the fit is
"good". Therefore, instead we will normalize the signal based on a value proportional to
the magnitude of the signal. Considering the tendency of FMRI noise to have large unexplainable
peaks and troughs, rather than using MAX and MIN values, I used a robust estimator of 
scale, the Median-Absolute-Deviation (MAD). Technically this is an estimator of the standard
deviation, however in this case it is also a good estimator of the scale of the input
signal. Thus, each point in the estimate as well as the original signal may be divided by
this, leading to a normalized signal. Instead, however, I simply divided the 
$\sqrt{MSR}$ by the MAD, which is functionally equivalent but leaves the  BOLD
levels intact for further analysis. The normalized square root MSR values are 
shown in \autoref{tab:SignleVoxelActivationComparison}.

Comparing the results of \autoref{sec:HighNoise} and \autoref{sec:PureNoiseHighMag}, it is
clear that distinguishing between these cases is a difficult prospect. One possibility
is to just allow the particle filter to fail when particle deprivation occurs; however,
as discussed in the previous section, that could open the door to more false negatives.
Naturally there is a noise ceiling above which it will be impossible to determine model 
validity. The fact
that the particle filter is able to get close to the "true" signal is sadly irrelevant
when the noise is this high.
Ultimately, a threshold well below those shown in the high noise case 
will have to be placed on the error, if any confidence is going to be placed in
the results. Luckily the "high noise" case featured in \autoref{sec:HighNoise}
is actually noisier than typical FMRI.

@@

It is again clear that a single point estimate of the parameters is not feasible,
but rather a distribution of parameters is the best any modeling algorithm
is going to be capable of for this version of the BOLD signal. In spite of
this, and relatively heavy noise, the fact that is that the fits were
good. Clearly, from the normalized $\sqrt{MSR}$ it is possible to identify
 \"active" regions; or regions that respond the way the BOLD model expects.
Although some of the fits in the  \"active" regions did not have good regression,
this is not necessarily the work of false negatives. Instead, because possum
simulates different tissues, it is more likeley that those regions non
grey-matter areas. Essentially these areas should not have reacted very strongly
because in the real world such regions wouldn't. By the fact that it 
was relatively easy to identify the regions of activation from the simulated 
results, something similar should happen with real FMRI data, which is discussed
in the next session. which

>>>>

\chapter{Simulation}
\label{sec:SimulationResults}
Two levels of simulation are discussed in this section. First the simulation of single time series
and second, a slice of simulated FMRI time series. The single time series tests
are necessary to investigate the power of particle filters in 
identifying the BOLD model in a noisy environment. If the particle filter is unable
to get back to the \emph{true} time-series in spite of noise then the particle filter
will not be useful. Additionally, determination of reasonable parameters from the
time-series is also desirable. The reason to then simulate an entire slice is that
Physics-Oriented Simulated Scanner for Understanding MRI (POSSUM)
models noise more realistically, for instance by noise in the frequency domain. Additionally 
it provides insight into the applicability of particle filters in modeling the BOLD 
signal on a large scale. Both sorts of tests are usefull in determining the
consistency of the particle filter. For the single voxel tests, each test will
actually be performed eleven different times, each with a new noise realization.
If runs fail to have consistent estimates of the underlying BOLD signal, then
this would indicate a large variance error in the model. Similarly, in the
Possum simulation there are actually only four discrete parameter sets driving the time-series.
Nevertheless each voxel will have a different tissue composition and a different
noise realization. Therefore the Possum simulation should also provide a good
test of the consistency of the BOLD model.

\section{Single Time Series}
\label{sec:Single Voxel Simulation}
Given the state-space equations for the BOLD signal, simulating a single time 
series is relatively straight forward. After a true signal is generated,
identically and independently distributed (I.I.D.) Gaussian noise and a Wiener
process with Gaussian I.I.D. steps are added to the true signal. Finally a 
carrier level is added, since BOLD is typically
measured as a \% difference from the baseline. The particle filter
algorithm will immediately remove this by calculating the \% difference, 
but adding a carrier level means that the exact same algorithm which 
will is used for simulated data may be used for the real data.

Once this noisy simulated time series has been generated, the particle filter algorithm
 is then run on this single time series image. Here I will include two sets of tests 
to determine the power of the particle filter in modeling. The first set are 
used to demonstrate the ability of the particle filter to find the most likely
set of parameters/state variables over the course of the run. The second type
of test will investigate the problem of false-positives. As the first
round of tests will show, given that there is an underlying BOLD signal, 
the particle filter is excellent at finding the most probable cause of 
the observed signal. However, as discussed in the false positive tests,
even if there is no true underlying signal, the particle filter will still determine
the most likely BOLD signal; which may not be flat. Thus, it is 
important to investigate methods of determining false positives using 
average residuals. This problem could in actuality never come up, for instance
if the number of measurements is very large or if the noise peaks are not
particularly large.

@@

To begin the single voxel simulation; I generated a signal using the following parameters:
$\{\tau_0 = 1.45, \alpha = .3, E_0 = .47, V_0 = .044, \tau_s = 1.94, \tau_f = 1.99, \epsilon = 1.8\}$.
These same parameters will be used again in the high noise case. The noise realizations were
then based on a measurement noise, $\sigma_y$, of $.001$ and a drift standard deviation,
$\sigma_x$ of $.0005$. The measurement noise as well as the steps of the drift
were taken to be Gaussian
For this low noise case, the eleven realizations are shown in \autoref{fig:LowNoiseRealization}.
The actual signal that was delivered into the particle filter
is the result of some preprocessing to remove drift, as described in 
\autoref{sec:Methods Preprocessing}. The bias introduced into the signal by preprocessing 
may have some effect on the resulting fit; thus the preprocessed signal is compared
to the true BOLD signal in \autoref{fig:PreprocessedLowNoise}.
The preprocessing consists of several steps, which are discussed in detail in \autoref{sec:Methods Preprocessing}.
Obviously the spline struggles to match the signal near the end, as the graph shows, although 
overall, the preprocessing seems to have been successful at removing trends. Finally, the 
set of fits to the true BOLD signal are shown in \autoref{fig:FitComparisonLowNoise}.
The filtering property of the particle filter is clear from the results here.  In several locations the output
of the particle filter looks like a filtered version of the input. For instance toward the
end, the estimates stay flat in spite of the preprocessed data drifting off. By
this point, the algorithm has converged sufficiently to know that that such a movement in
signal isn't possible. A similar circumstance occurs at 100 seconds in. 
In general the fits are good, although the bias introduced by pre-processing clearly
results in a slightly larger peak signal. The final parameter sets are shown in 
\autoref{tab:LowNoiseResults}. Note that throughout the results, unless otherwise specified,
I will define the residual as the square root of the mean squared residual, 
\begin{equation}
\text{Residual} = \sqrt{\sum (\hat{y}_k - y_k)^2}
\end{equation}
where $\hat{y}_k$ is the estimated output at time $k$ and $y_k$ is the output
sample at time $k$. Note the subtle distinction between this and the error
which I will define as 
\begin{equation}
\text{Error} = \sqrt{\sum (\hat{y}_k - Y_k)^2}
\end{equation}
where $\hat{y}_k$ is the estimated output, and $Y_k$ is the underlying (free of noise)
output. Throughout this section and the next, error and residual of a time series 
will be referencing these values.

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline 
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & $\sqrt{MSR}$ &$\sqrt{MSE}$\\
\hline 
\rowcolor[gray]{.8}
1.45 & .3 & .47 & .044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline 
\hline 
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.009876  \\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.009932  \\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.009680  \\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.009120  \\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.009713  \\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.009485  \\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.010219  \\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.010080  \\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.010329  \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.010015  \\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.009505  \\
\hline                                                                           
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.009814 \\
\hline 
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise. First row is the true parameters,
last is mean over the 11 runs. The $\sqrt{MSR}$ is residual and $\sqrt{MSE}$ is the error.}
\label{tab:LowNoiseResults} 
\end{table}

@@

The parameters arrived at for all ten filter runs are shown in \autoref{tab:HighNoiseResults}.
Clearly the additional noise have resulted in much more sporadic results. This is often the 
result when the particle filter converges too fast, a result of the weighting functions' variance
being significantly smaller than the measurement noise ($.005$ vs. $.01$). The error
certainly suffers due to this effect.

%NO SIGNAL, LOW NOISE
\subsection{Pure-Noise, low magnitude}
\label{sec:PureNoiseLowMag}
The two final single-voxel tests force the particle filter to attempt to learn a noise-only
time series. In the first test the noise used will be the same as that from the \autoref{sec:HighNoise},
$\sigma_x = .01, \sigma_y = .005$. The parameters will be set the same as well, but the
stimulus/input will be set to 0 the entire time. In effect it is a region of the brain for
which no visual stimulus induces activity. For the particle filter, on the other hand,
the stimulus will be left as in the previous two sections. The question then is how the
particle filter will respond to signal that does not correlate with the input, and how
the output may be differentiated from a time series that does. The time series'
are shown in \autoref{fig:NoiseOnly}, the preprocessed versions are shown in \autoref{fig:PreprocessedNoiseOnly}.
The line fits are shown in \autoref{fig:fits_noiseonly}.

@@

As before, the convergence all seems to follow a similar path, leaving almost no
variance in the estimated time series (\autoref{fig:fits_noiseonly_high}). Now, however
the peaks are comparable to peaks in a real timeseries. Interestingly the algorithm
suffered from almost constant particle deprevation, meaning that the heuristic
for rescuing the particle filter from particle deprivation, discuessed in
\autoref{sec:Resampling} in fact was working against the proper course of action. Of course
 the proper course of action in this case would be for the particle filter to fail,
 since no particle can really properly estimate a random sequence. When this mechanism
 was removed, all 11 runs stopped due to particle deprevation (all weights hit zero). 
 The problem with allowing particle deprivation to occur is that it can \emph{rarely}
 occur if the prior happens to not be dense enough in the area of the solution. Thus,
 there is an issue of false positives vs. false negatives. A middle ground, such as 
 allowing deprivation to occur if the recovery mechanism has already triggered once
 may be an acceptable compromise, however it would be difficult to strike the 
 right balance. Instead for the purposes here we depend on the square root MSR to 
 evaluate if the results were reasonable or not.

@@

The first step in determining the validity of a model to provide and order of quality
to rate the results by. Unfortunately, because of the variablity in the signal levels the
raw $\sqrt{MSR}$ cannot perform this task. As demonstrated by \autoref{sec:PureNoiseLowMag},
just because the square-root mean-squared-residual is low doesn't mean the fit is
good. Therefore, instead we will normalize the signal based on a value proportional to
the magnitude of the signal. Considering the tendency of FMRI noise to have large unexplainable
peaks and troughs, rather than using MAX and MIN values, I used a robust estimator of 
scale, the Median-Absolute-Deviation (MAD). Technically this is an estimator of the standard
deviation, however in this case it is also a good estimator of the scale of the input
signal. Thus, each point in the estimate as well as the original signal may be divided by
this, leading to a normalized signal. Instead, however, I simply divided the 
$\sqrt{MSR}$ by the MAD, which is functionally equivalent but leaves the  BOLD
levels intact for further analysis. The normalized square root MSR values are 
shown in \autoref{tab:SignleVoxelActivationComparison}.

Comparing the results of \autoref{sec:HighNoise} and \autoref{sec:PureNoiseHighMag}, it is
clear that distinguishing between these cases is a difficult prospect. One possibility
is to just allow the particle filter to fail when particle deprivation occurs; however,
as discussed in the previous section, that could open the door to more false negatives.
Naturally there is a noise ceiling above which it will be impossible to determine model 
validity. The fact
that the particle filter is able to get close to the true signal is sadly irrelevant
when the noise is this high.
Ultimately, a threshold well below those shown in the high noise case 
will have to be placed on the error, if any confidence is going to be placed in
the results. Luckily the high noise case featured in \autoref{sec:HighNoise}
is actually noisier than typical FMRI.

@@

It is again clear that a single point estimate of the parameters is not feasible,
but rather a distribution of parameters is the best any modeling algorithm
is going to be capable of for this version of the BOLD signal. In spite of
this, and relatively heavy noise, the fact that is that the fits were
good. Clearly, from the normalized $\sqrt{MSR}$ it is possible to identify
 active regions; or regions that respond the way the BOLD model expects.
Although some of the fits in the  active regions did not have good regression,
this is not necessarily the work of false negatives. Instead, because possum
simulates different tissues, it is more likeley that those regions non
grey-matter areas. Essentially these areas should not have reacted very strongly
because in the real world such regions wouldn't. By the fact that it 
was relatively easy to identify the regions of activation from the simulated 
results, something similar should happen with real FMRI data, which is discussed
in the next session. which
